% Copyright (c) 1988 Massachusetts Institute of Technology
%	$Source: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/comm-windowgram.tex,v $
%	$Author: jtkohl $
%	$Header: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/comm-windowgram.tex,v 2.0 1989/04/05 15:50:20 jtkohl Exp $
%
\subsection{Communicating with the WindowGram Client}
\label{comm-zwgc}

The following sections describe control notices that can be
sent to a WindowGram client to ask it to perform various functions.

\subsubsection{Where to Send Notices}

Notices should be sent to the WindowGram's port on the local machine.
Thus the destination address should be set with code such as:

\begin{code}
    struct sockaddr_in newsin;

    newsin = ZGetDestAddr();
    newsin.sin_port = (unsigned short) ZGetWGPort();
    ZSetDestAddr(&newsin);
\end{code}
(Of course, suitable error checking should be included.)

\subsubsection{Available Commands}

The following functions are available.  They are listed in the form
[kind, class, instance, opcode].  The rest of the notice ({\em e.g.\/}
the message body) has no effect on the requested action.

\begin{itemize}
\item {[UNSAFE, WG_CTL_CLASS, WG_CTL_USER, USER_REREAD]}: Reread the
user's \filename{.zephyr.desc} file.
\item {[UNSAFE, WG_CTL_CLASS, WG_CTL_USER, USER_SHUTDOWN]}: Save
subscriptions, unsubscribe to all notices, and cease processing all
incoming notices except a USER_STARTUP control notice.
\item {[UNSAFE, WG_CTL_CLASS, WG_CTL_USER, USER_STARTUP]}: Re-subscribe
to saved subscriptions, and continue processing incoming notices (this
is only useful after a USER_SHUTDOWN request.).
\end{itemize}

\subsubsection{Sample Application}

This application demonstrates sending a control notice to a WindowGram
client to ask it to re-read the user's \filename{.zephyr.desc} file.  It
initializes the library, changes the destination address to the
WindowGram client's port, fills in the control notice, and sends it off.
It does not wait for any acknowledgement.

\begin{code}
#include <zephyr/zephyr.h>

main()
{
    ZNotice_t notice;
    struct sockaddr_in newsin;
    Code_t retval;
    int newport;

    /* Initialize the library */
    if ((retval = ZInitialize()) != ZERR_NONE) {
        com_err("sample", retval, "while initializing");
        exit (1);
    }

    /* Change the destination to be the user's WindowGram client */
    newsin = ZGetDestAddr();
    if ((newport = ZGetWGPort()) == -1) {
        fprintf(stderr, "Can't find WindowGram port\n");
        exit (1);
    }
    newsin.sin_port = (unsigned short) newport;
    ZSetDestAddr(&newsin);

    bzero((char *)&notice, sizeof(notice));
    /* initialize the notice after zeroing the entire structure */
    /* Fill in notice for a REREAD command */
    notice.z_kind = UNSAFE;
    notice.z_port = 0;
    notice.z_class = WG_CTL_CLASS;
    notice.z_class_inst = WG_CTL_USER;
    notice.z_opcode = USER_REREAD;
    notice.z_sender = 0;
    notice.z_recipient = "";
    notice.z_default_format = "";
    notice.z_message = "";
    notice.z_message_len = 0;

    /* Send the command */
    if ((retval = ZSendNotice(&notice, ZNOAUTH)) != ZERR_NONE) {
        com_err("sample", retval, "while sending notice");
        exit (1);
    }
    exit(0);
}
\end{code}
