% Copyright (c) 1988 Massachusetts Institute of Technology
%	$Source: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/introduction.tex,v $
%	$Author: jtkohl $
%	$Header: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/introduction.tex,v 2.0 1989/04/05 15:52:46 jtkohl Exp $
%
\section{Introduction}
\label{introduction}

\Zephyr\ is a notice transport and delivery system developed at MIT
Project Athena in 1987.  It is an integrated system that provides the
ability to send notifications, such as personal messages and system
warnings, from one user or system service to another user or group of
users.

This manual describes the \Zephyr\ library, the programmer's interface
to \Zephyr.  The \Zephyr\ library consists of a collection of C
language functions which allow the programmer to send and receive
notices.  Additional functions are provided in the library to modify
how notices are distributed and to retrieve various pieces of
information.

Because this manual is primarily concerned with describing how to
write an application which uses \Zephyr, the internal workings of the
\Zephyr\ system are not discussed in detail.  The interested reader
can find additional information about \Zephyr\ in the \Zephyr\ design
document \cite{zephyr-design}.

This manual is organized into four main sections as follows:

\begin{description}
\item {\bf Overview of the \Zephyr\ System}.  This
section describes the various components of \Zephyr, and briefly
describes how they interact.

\item {\bf General Concepts}.  This
section describes the subscription and user location services.

\item {\bf Programming Standard
Applications}.  This section describes the \Zephyr\ include files,
the functions available in the \Zephyr\ library, and many concepts
that are relevant to programming \Zephyr\ applications.

\item {\bf Advanced Programming
Topics}.  This section describes more advanced topics, including how
to send control messages to \Zephyr\ servers and HostManagers.
\end{description}

In addition, the following appendices are provided:

\begin{description}
\item {\bf Additional Examples}.  Listings of
{\bf zwrite}, {\bf zlocate}, and {\bf zstat}, three standard \Zephyr\
applications, are provided.
\item {\bf Error Codes}.  All \Zephyr\ error codes are
listed with a brief description of each.
%\item {\bf Predefined Notice Formats}.  Contains notice formats
%which are currently in use by \Zephyr\ applications or which are used
%internally by the \Zephyr\ system.
\item {\bf Function Templates}.  Contains the templates
for all of the functions mentioned in this manual.
\end{description}
