% Copyright (c) 1988 Massachusetts Institute of Technology
%	$Source: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/library.tex,v $
%	$Author: jtkohl $
%	$Header: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/library.tex,v 2.1 1989/06/29 16:39:02 jtkohl Exp $
%
\subsection{The Zephyr Library and Include Files}
\label{library-include}
% what a gross hack: this is to make the _ appear; they don't in the
% Courier fonts (PostScript)
\font\twlttreal  = cmtt12               % typewriter
    \hyphenchar\twlttreal = -1         %  suppress hyphenation in \tt font

Applications that want to use the features of \Zephyr\ must link
against the \Zephyr\ library and the com_err library, and possibly the
Kerberos library and DES library.  The \Zephyr\ library contains the functions
defined in the later sections of this document.  It is usually called
{\tt libzephyr.a}, and may be included in an application by specifying
{\tt -lzephyr} on the compile or link line.  

The com_err library contains error-reporting functions (See the com_err
design document \cite{comerr-paper}.).  It is usually called {\tt \twlttreal
libcom_err.a}, and may be included in an application by specifying {\tt
\twlttreal -lcom_err} on the compile or link line.

The Kerberos library contains Kerberos functions.  It is usually called
{\tt libkrb.a}, and may be included in an application by specifying
{\tt -lkrb} on the compile or link line.

The DES library contains DES functions.  It is usually called
{\tt libdes.a}, and may be included in an application by specifying
{\tt -ldes} on the compile or link line.

The main \Zephyr\ include file, {\tt zephyr.h}, must also be included
in all source files that use \Zephyr\ functions.  It contains many
\Zephyr-related definitions, and will automatically include
zephyr_err.h, the file that contains the error code definitions, plus
the system include files $<$errno.h$>$, $<$sys/types.h$>$,
$<$netinet/in.h$>$, $<$sys/time.h$>$, and $<$stdio.h$>$, and if Kerberos
is enabled, $<$krb.h$>$.
{\tt zephyr.h} may be included by specifying the line {\tt \#include
$<$zephyr/zephyr.h$>$} in the source file.

In order for your programs to interact properly with the \Zephyr\
library provided on Project Athena, you {\em must\/} specify the {\tt
-DKERBEROS} option to the C compiler when compiling your code.

\subsubsection{Naming conventions}
\label{naming-conventions}
All routines internal to the Zephyr library are named beginning with
``Z_''.  All routines intended to be used by applications programmers are
named beginning with ``Z'' and do not contain any underscores (_).
