% Copyright (c) 1988 Massachusetts Institute of Technology
%	$Source: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/locator.tex,v $
%	$Author: jtkohl $
%	$Header: /tmp/git-rcsimport-Ge1GfW1M7y/rcs/locator.tex,v 2.0 1989/04/05 15:53:45 jtkohl Exp $
%
\subsection{The User Location Service}
\label{user-location}

In addition to storing subscription information about each user, the
\Zephyr\ servers maintain a database of the location of each
currently logged-in user.  This information is not used by the servers to
determine where to send notices---a client can subscribe to notices
without being registered in the location database---but is made
available to other users for personal use.

Normally a user is registered by a standard client application (such
as the WindowGram client) upon login, and is deregistered at logout.
However, an application may occasionally desire to modify or remove
user location information from the database.  The ZSetLocation
function (\myref{ZSetLocation}) will do this.

\subsubsection{Location Information}

The following information is stored by the \Zephyr\ servers for each
registered user:

\begin{itemize}
\item The name of the host the user is registered from.
\item The name of the terminal the user is using; on a workstation that
supports the X window system, this may be the display name instead.
\item The date and time the user was registered.
\end{itemize}

\subsubsection{Exposure Levels}
\label{exposure-levels}

A user can register at any of a number of {\em exposure levels\/}.  An
exposure level tells the servers who will be able to access
information about the user's location, and whether or not the
registration will be announced to other users.  When a registration
can be announced to other users, the \Zephyr\ server sends it to users
subscribing to \triple{\sc LOGIN}{{\em user}}{*}, where {\em user\/} is a
fully qualified Kerberos principal ({\em user@realm}).  If Kerberos is
not in use, the user field will be {\em user@host}.

The following exposure levels are defined:

\begin{itemize}
\item {\bf None:} The user's location information is completely hidden, and the
registration is not announced.
\item {\bf Opstaff:} Only members of the site's operational staff can
retrieve the user's location information, and the registration is not
announced.
\item {\bf Realm-Visible:} Only users authenticated in the local
Kerberos realm can retrieve the user's location information, and the
registration is not announced.
\item {\bf Realm-Announced:} Only users authenticated in the local
Kerberos realm can retrieve the user's location information, and the
registration is announced to all interested users in the local realm.
\item {\bf Net-Visible:} All users can retrieve the user's location
information.  The registration is announced to all interested users
in the local realm. 
\item {\bf Net-Announced:} All users can retrieve the user's location
information, and the registration is announced to all interested users.
\end{itemize}
When Kerberos is not enabled, each host is interpreted as a separate
realm for purposes of exposure levels and login notices.
